Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-06-07 review/response.Rmd

### Associate Editor:

The submission has been evaluated by two reviewers. The manuscript is well written and organized. I have some more philosophical issues in addition to those raised by the two reviewers.

The authors need to convince readers (users) this kind of environment is good for daily EDA for the real world of big data/data science.

**We have revised the introduction to improve the motivation to make this clear.**

@@

Example(s) with very large number (at least hundreds) of dimensions should be included in the study.

**The simulation study and the applications reveal that the current methods are efficient only in smaller parameter spaces, there are two components that would be required to scale it to examples with hundreds of dimensions: (1) fast computational engine, (2) an efficient optimiser. Both of these would require major implementation work. We have explained this now in the discussion section.** XXX check, add to discussion

**As we now explain in the introduction, we have previously considered an example where the dimensionality was around 60, and it worked best to reduce the dimensionality using PCA as a pre-processing step, because this explained most of the variability (Cook, Laa, and Valencia 2018).**

@@

Review report for "Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics"

This manuscript presented a simulation study to visually explore the properties of a set of projection pursuit indexes (PPIs) using a grand tour based on the five criterions. The selected PPIs were then applied to two real datasets in physics for revealing potential patterns. In general I found this article was well written and it fully addresses the problems to be solved. I have no major issue. Some specific comments are listed below:

1) Authors conducted the simulation study to evaluate the selected PPIs based on the five criterions and the results were summarized into Table 3. On the other hand, authors may consider another table that summarizes the advantages/disadvantages/characteristics of these mathematical indexes from the previous literatures. This review is helpful for users to comprehend these indexes' properties.

**This comparison was the subject of the thesis Grimm (2016). We have now added a brief summary of these findings at the end of section 2.2.**

### 2019-06-07 scagnostics.Rmd
Working on the introduction.

>>>>

\textcolor{red}{The same methods can also be used to explore larger datasets with hundreds of dimensions, as common in real world examples. In these scenarios it is best to reduce the number of dimensions before applying projection pursuit. For example in [@Cook:2018mvr] a 56 dimensional parameter space was reduced to the first six principal components before applying tour methods for the identification of multivariate relationships, revealing previously overlooked features. On the other hand, applying projection pursuit directly to the high-dimensional dataset is generally limited by the availability of an efficient optimiser.
}
